{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-05 thesis/education.tex
more llama

\begin{itemize}
	\item Finds the declaration of {\tt ready\_list}, the scheduler runqueue declared by the basecode,
		%and detects if the student has modified to be an array of lists rather than a single one.
		\revisionminor{and detects if the student has replaced the default definition
		with a different name and/or data structure.}
		If so,
		%defines the length of that array in a macro to be used by {\tt is\_runqueue()}
		\revisionminor{emits macros to configure {\tt is\_runqueue()}'s behaviour to handle
		certain common alternate approaches}
		(part of the patch described below).
		Either way defines a function {\tt get\_rq\_addr()} to return the address of the %(first)
		list.
	\item Changes the basecode's definition of {\tt TIME\_SLICE} from 4 to 1 (units of timer ticks)
		so Landslide's timer injection will properly drive the context switcher.
	\item Inserts {\tt tell\_landslide\_forking()} into {\tt thread.c}
		(using {\tt sed} rather than the patch, described below,
		because it must go in a function which students have to implement,
		which is likely to disturb the context and make a patch fail).
	\item Adds the new {\tt priority-donate-multiple} test.
	\item Applies the {\tt annotate-pintos.patch} patch to the imported student implementation, which:
	\begin{itemize}
		\item Adds {\tt tell\_landslide\_thread\_on\_rq()}
			and {\tt tell\_landslide\_thread\_off\_rq()}
			annotations
			to {\tt list\_insert()} and {\tt list\_remove()} respectively
			(in {\tt lib/kernel/\allowbreak{}list.c}, which the students don't modify),
			which
			check whether the argument list
			is the scheduler runqueue
			using a helper function {\tt is\_runqueue},
			which in turn uses {\tt get\_rq\_addr()} and {\tt READY\_LIST\_LENGTH} described above.
		\item Modifies the existing {\tt priority-sema} and {\tt alarm-simultaneous} tests to be more Landslide-friendly.
		\item Inserts the {\tt tell\_landslide\_sched\_init\_done()},
			{\tt tell\_landslide\_vanishing()},
			and {\tt tell\_landslide\_thread\_switch()}
			annotations in the appropriate places
			(which the students generally do not modify).
	\end{itemize}
	\item Detects if the student has renamed the {\tt elem} field of the TCB struct,
		and if so renames its use in {\tt is\_runqueue()} (described above) correspondingly.
	\item Detects if the student has renamed the {\tt cur} (currently running thread) variable
		in the context switcher, and if so renames it back.
\end{itemize}

>>>>

\begin{itemize}
	\item Finds the declaration of {\tt ready\_list}, the scheduler runqueue declared by the basecode,
		%and detects if the student has modified to be an array of lists rather than a single one.
		\revisionminor{and detects if the student has replaced the default definition
		with a different name and/or data structure.}
		If so,
		%defines the length of that array in a macro to be used by {\tt is\_runqueue()}
		\revisionminor{emits macros to configure {\tt is\_runqueue()}'s behaviour to handle
		certain common alternate approaches}
		(part of the patch described below).
		Either way defines a function {\tt get\_rq\_addr()} to return the address of the %(first)
		list.
	\item Changes the basecode's definition of {\tt TIME\_SLICE} from 4 to 1 (units of timer ticks)
		so Landslide's timer injection will properly drive the context switcher.
	\item Inserts {\tt tell\_landslide\_forking()} into {\tt thread.c}
		(using {\tt sed} rather than the patch, described below,
		because it must go in a function which students have to implement,
		which is likely to disturb the context and make a patch fail).
	\item Adds the new {\tt priority-donate-multiple} test.
	\item Applies the {\tt annotate-pintos.patch} patch to the imported student implementation, which:
	\begin{itemize}
		\llitem Adds {\tt tell\_landslide\_thread\_on\_rq()}
			and {\tt tell\_landslide\_thread\_off\_rq()}
			annotations
			to {\tt list\_insert()} and {\tt list\_remove()} respectively
			(in {\tt lib/kernel/\allowbreak{}list.c}, which the students don't modify),
			which
			check whether the argument list
			is the scheduler runqueue
			using a helper function {\tt is\_runqueue},
			which in turn uses {\tt get\_rq\_addr()} and {\tt READY\_LIST\_LENGTH} described above.
		\llitem Modifies the existing {\tt priority-sema} and {\tt alarm-simultaneous} tests to be more Landslide-friendly.
		\llitem Inserts the {\tt tell\_landslide\_sched\_init\_done()},
			{\tt tell\_landslide\_vanishing()},
			and {\tt tell\_landslide\_thread\_switch()}
			annotations in the appropriate places
			(which the students generally do not modify).
	\end{itemize}
	\item Detects if the student has renamed the {\tt elem} field of the TCB struct,
		and if so renames its use in {\tt is\_runqueue()} (described above) correspondingly.
	\item Detects if the student has renamed the {\tt cur} (currently running thread) variable
		in the context switcher, and if so renames it back.
\end{itemize}
